Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
reponse commentaire
retrait TODO
linearisation
fix typos

We could use ``widening up to'' or ``widening with thresholds'', propagating the ``magic values'' $\pm 100000$ associated to \lstinline|x| into~\lstinline|x_old|, but these syntactic approaches cannot directly cope with programs for which $\lstinline|x|  \in [-100000,+100000]$ is itself obtained by analysis.
The guided static analysis of \citet{DBLP:conf/sas/GopanR07} does not perform
better, and also obtains $\verb|x_old| \in (-\infty,+\infty)$.

@@

Guided static analysis from \citet{DBLP:conf/sas/GopanR07} yields at line 5
$\lstinline|x_old| \in~]-\infty,+\infty[$.
Path-focusing \citep{Monniaux_Gonnord_SAS11} performs slightly
better, and finds $\lstinline|x_old| \in~]-\infty,10000]$.

>>>>

We could use ``widening up to'' or ``widening with thresholds'', propagating the ``magic values'' $\pm 100000$ associated to \lstinline|x| into~\lstinline|x_old|, but these syntactic approaches cannot directly cope with programs for which $\lstinline|x|  \in [-100000,+100000]$ is itself obtained by analysis.
The guided static analysis of \citet{DBLP:conf/sas/GopanR07} does not perform
better, and also obtains $\lstinline|x_old| \in (-\infty,+\infty)$.

@@

Guided static analysis from \citet{DBLP:conf/sas/GopanR07} yields at line 5
$\lstinline|x_old| \in (-\infty,+\infty)$.
Path-focusing \citep{Monniaux_Gonnord_SAS11} performs slightly
better, and finds $\lstinline|x_old| \in (-\infty,10000]$.
